\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-17 ms/adult.tex
Update
Update top 25 sites
Minor formatting. Also added top 25 non-adult sites

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[width=.55\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
\caption*{\footnotesize \emph{Notes:} 
	Hours spent on adult sites by individuals who consumed pornography in the sample period.
	Individuals are split into deciles with each bin containing approximately the same number of individuals.
	Height of bars indicate mean of each bin.
	Capped vertical bars are 95\% confidence intervals.
	See \cref{tab:distribution_duration} for the more tabulated values.
}
\label{fig:distribution_duration}
\end{figure}

@@

\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\begin{figure}[h]
\centering
\caption{Proportion of Visits to Pornographic Sites}
\includegraphics[scale=.75]{../figs/top_25_adultsites.pdf}
\label{fig:top25}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\caption{Distribution of Consumption of Pornography Online}
\includegraphics[width=.5\linewidth]{../figs/distribution_duration_on_adultsites.pdf}
\caption*{\footnotesize \emph{Notes:} 
	Hours spent on adult sites by individuals who consumed pornography in the sample period.
	Individuals are split into deciles with each bin containing approximately the same number of individuals.
	Height of bars indicate mean of each bin.
	Capped vertical bars are 95\% confidence intervals.
	See \cref{tab:distribution_duration} for the more tabulated values.
}
\label{fig:distribution_duration}
\end{figure}

@@

\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}cc@{\hspace{0\tabcolsep}}}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex} \\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\begin{figure}[h]
	\centering
	\caption{Top 25 Adult Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
		\caption*{\footnotesize \emph{Notes:} 
			Table shows the top 25 adult sites that panelists visit in the sample period.
			Adult sites are categorized by YouGov.
			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  
			Sites to the right of the vertical dashed are the top 1 percent.
		}
	\label{fig:top25_adult}
\end{figure}

\begin{figure}[h]
	\centering
	\caption{Top 25 (Non-Adult) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
		\caption*{\footnotesize \emph{Notes:} 
			Table shows the top 25 non-adult sites that panelists visit in the sample period.
			The \emph{Hours} column are the total number of hours that panelists in the sample spent on the site. 
			The \emph{Visits} column is total number of visits by panelists in the sample to the site.  			
			Sites to the right of the vertical dashed are the top 1 percent.
		}
	\label{fig:top25_nonadult}
\end{figure}
